### 2017-05-31 doc/intro.tex
minor

\begin{abstract}
  We present novel methods for analyzing the activation patterns of
  RNNs from a linguistic point of view and explore the types of 
  linguistic structure they learn. As a case study, we use a multi-task gated
  recurrent network architecture consisting of two parallel pathways with
  shared word embeddings trained on predicting the
  representations of the visual scene corresponding to an input
  sentence, and predicting the next word in the same sentence, 
  in addition to a standard standalone language model. 
  We propose a method for estimating the amount of contribution
  of individual tokens in the input to the final prediction of the networks.   
  Using this method, we show that the image prediction pathway pays
  selective attention to lexical categories and grammatical functions
  that carry semantic information, and also learns to treat word types 
  differently depending on their grammatical function and their position 
  in the sequential structure of the sentence. In contrast, the language 
  models are comparatively more sensitive to words with a syntactic 
  function. Further analysis of the most informative n-gram contexts for 
  each model shows that in comparison to the image prediction pathway,
  the language models react more strongly to abstract contexts 
  that represent syntactic constructions. 
%  Furthermore, we propose methods to explore the function
%  of individual hidden units in RNNs and show that the two pathways
%  of the architecture in our case study contain
%  specialized units tuned to patterns informative
%  for the task, some of which can carry activations to later time
%  steps to encode long-term dependencies.

>>>>

\begin{abstract}
  We present novel methods for analyzing the activation patterns of
  RNNs from a linguistic point of view and explore the types of 
  linguistic structure they learn. As a case study, we use a multi-task gated
  recurrent network architecture consisting of two parallel pathways with
  shared word embeddings trained on predicting the
  representations of the visual scene corresponding to an input
  sentence, and predicting the next word in the same sentence, 
  in addition to a standard standalone language model. 
  We propose a method for estimating the amount of contribution
  of individual tokens in the input to the final prediction of the networks.   
  Using this method, we show that the image prediction pathway pays
  selective attention to lexical categories and grammatical functions
  that carry semantic information, and learns to treat word types 
  differently depending on their grammatical function and their position 
  in the sequential structure of the sentence. In contrast, the language 
  models are comparatively more sensitive to words with a syntactic 
  function. Further analysis of the most informative n-gram contexts for 
  each model shows that in comparison to the image prediction pathway,
  the language models react more strongly to abstract contexts 
  that represent syntactic constructions. 
%  Furthermore, we propose methods to explore the function
%  of individual hidden units in RNNs and show that the two pathways
%  of the architecture in our case study contain
%  specialized units tuned to patterns informative
%  for the task, some of which can carry activations to later time
%  steps to encode long-term dependencies.
